Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2022-01-05 paper/paper.tex
minor change to intro again to highlight difference in tensor element types

%more concretely, an maximal independent set of a graph $G$ corresponds to a maximum clique in the complement graph of $G$,
%and the complement vertex set of an MIS corresponds to a minimum vertex cover of the graph $G$.
%In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
\blue{We need to distinct ourself in the problem we want to solve.}
In this paper, we introduce a generic programming tensor-network framework to compute the various \textit{properties} pertaining to independent sets. 
%In this paper, we do not limit our study to just finding an MIS and its size. 
% We introduce a tensor-network based framework to compute the various \textit{properties} pertaining to independent sets.
Beyond just finding an MIS and its size as described above, these properties also include, for example, the number and enumeration of independent sets or maximal independent sets of a given size.
We map these independent set problems into generic tensor network contraction with specially designed tensor element algebra.
% There are many other interesting problems pertaining to independent sets, such as the number of independent sets of a given size
% and enumerating independent sets at a give size or what we call computing \textit{properties}.
Some of these problems are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022} \red{replace with experiment paper when ready};
they can, for example, be used to understand phase transitions, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.

>>>>

%more concretely, an maximal independent set of a graph $G$ corresponds to a maximum clique in the complement graph of $G$,
%and the complement vertex set of an MIS corresponds to a minimum vertex cover of the graph $G$.
%In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
\blue{We need to distinct ourself in the problem we want to solve.}
In this paper, we introduce a generic programming tensor-network framework to compute the various \textit{properties} pertaining to independent sets. 
%In this paper, we do not limit our study to just finding an MIS and its size. 
% We introduce a tensor-network based framework to compute the various \textit{properties} pertaining to independent sets.
Beyond just finding an MIS and its size as described above, these properties also include, for example, the number and enumeration of independent sets or maximal independent sets of a given size.
% There are many other interesting problems pertaining to independent sets, such as the number of independent sets of a given size
% and enumerating independent sets at a give size or what we call computing \textit{properties}.
Some of these problems are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022} \red{replace with experiment paper when ready};
they can, for example, be used to understand phase transitions, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}. We map the computation of these independent set properties into generic tensor network contraction with specially designed tensor element algebra. This is different from standard tensor network methods, where tensor elements are restricted to standard number types such as floating point numbers and integers.
